---
title: "EDA on Google Play Store Reviews"
author: "Nilesh Mani & Yogesh"
format: html
---

## Team Details

Team Number: 26 Team Name: Data Detectives

Members:\
1. Nilesh Mani (1NT23IS143)\
2. Yogesh (1NT23IS254)

## Section: C, D

# Load Libraries

```{r}
packages <- c("ggplot2","dplyr","ggridges","plotly")

for(p in packages){
  if(!require(p, character.only = TRUE)){
    install.packages(p)
    library(p, character.only = TRUE)
  }
}
```

```{r}
## Load Libraries
library(ggplot2)
library(dplyr)
library(plotly)
library(GGally)
library(ggridges)
```

## **Load Datasets**

```{r}
apps <- read.csv("C:/Users/acer/Downloads/LA1Files/googleplaystore.csv")
reviews <- read.csv("C:/Users/acer/Downloads/LA1Files/googleplaystore_user_reviews.csv")
```

## **Data Cleaning(Apps & Reviews)**

```{r}
## Data Cleaning
apps <- apps[!duplicated(apps), ]
apps <- apps[!is.na(apps$Rating), ]

apps$Installs <- gsub("[+,]", "", apps$Installs)
apps$Installs <- as.numeric(apps$Installs)

apps$Price <- gsub("\\$", "", apps$Price)
apps$Price <- as.numeric(apps$Price)

apps$Reviews <- as.numeric(apps$Reviews)

reviews <- reviews[!duplicated(reviews), ]
reviews <- na.omit(reviews)
```

## **Merge Datasets**

```{r}
df <- merge(apps, reviews, by="App")

head(df)
dim(df)
```

## **Visualisation**

## **APPS DATA**

```{r}
ggplot(apps, aes(Rating)) + geom_histogram()
ggplot(apps, aes(Category)) + geom_bar()
ggplot(apps, aes(Type)) + geom_bar()
ggplot(apps, aes(Content.Rating)) + geom_bar()
ggplot(apps, aes(Price)) + geom_histogram()
ggplot(apps, aes(Installs)) + geom_histogram()
ggplot(apps, aes(Reviews)) + geom_histogram()
ggplot(apps, aes(Rating)) + geom_density()
ggplot(apps, aes(Installs, Rating)) + geom_point()
ggplot(apps, aes(Reviews, Rating)) + geom_point()
```

## **RELATIONSHIPS**

```{r}
ggplot(apps, aes(Type, Rating)) + geom_boxplot()
ggplot(apps, aes(Category, Rating)) + geom_boxplot()
ggplot(apps, aes(Price, Rating)) + geom_point()
ggplot(apps, aes(Reviews, Installs)) + geom_point()
ggplot(apps, aes(Type, Installs)) + geom_boxplot()
ggplot(apps, aes(Content.Rating, Rating)) + geom_boxplot()
ggplot(apps, aes(Installs, Rating, color=Type)) + geom_point()
ggplot(apps, aes(Reviews, Rating, color=Category)) + geom_point()
ggplot(apps, aes(Installs, Rating)) + geom_smooth()
ggplot(apps, aes(Price, Reviews)) + geom_smooth()
```

## **REVIEWS DATA**

```{r}
ggplot(reviews, aes(Sentiment)) + geom_bar()
ggplot(reviews, aes(Sentiment_Polarity)) + geom_histogram()
ggplot(reviews, aes(Sentiment_Subjectivity)) + geom_histogram()
ggplot(reviews, aes(Sentiment_Polarity, Sentiment_Subjectivity)) + geom_point()
ggplot(reviews, aes(Sentiment, Sentiment_Polarity)) + geom_boxplot()
```

## **MERGED DATA**

```{r}
ggplot(df, aes(Sentiment, Rating)) + geom_boxplot()
ggplot(df, aes(Sentiment_Polarity, Rating)) + geom_point()
ggplot(df, aes(Sentiment, Installs)) + geom_boxplot()
ggplot(df, aes(Sentiment_Polarity, Installs)) + geom_point()
ggplot(df, aes(Installs, Rating)) + facet_wrap(~Type)
```

## **ADVANCED**

```{r}
numeric_df <- df[,c("Rating","Reviews","Installs","Price")]
heatmap(cor(numeric_df))

ggpairs(numeric_df)

ggplot(df, aes(Rating, Category)) + geom_density_ridges()

ggplot(df, aes(Category, Reviews)) + geom_boxplot()
ggplot(df, aes(Category, Price)) + geom_boxplot()
```

## **INTERPRETATION**

\`\`\`{## Insights}

-   Most apps have ratings between 4 and 4.5\
-   Free apps dominate the market\
-   Higher installs lead to more reviews\
-   Positive sentiment leads to higher ratings\
-   Price has little impact on app ratings\

```         

## **CONCLUSION**


## Conclusion

This report uses advanced visualization techniques to analyze app performance and user sentiment. The results show that installs and reviews are strongly correlated, while sentiment significantly impacts ratings.
```

## GitHub Repository

Link: <https://github.com/maninilesh258-coder/EDA-Google-PlayStore>
