---
title: "EDA on Google Play Store Reviews"
author: "Nilesh Mani & Yogesh"
format: html
---

## Team Details

Team Number: 26 Team Name: Data Detectives

Members:\
1. Nilesh Mani (1NT23IS143)\
2. Yogesh (1NT23IS254)

## Section: C, D

# Load Libraries

```{r}
## Load Libraries
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)

```

## **Load Datasets**

```{r}
apps <- read.csv("C:/Users/acer/Downloads/LA1Files/googleplaystore.csv")
reviews <- read.csv("C:/Users/acer/Downloads/LA1Files/googleplaystore_user_reviews.csv")
```

## **Basic Info**

```{r}
head(apps)
tail(apps)
dim(apps)
nrow(apps)
ncol(apps)
str(apps)
summary(apps)
names(apps)

head(reviews)
tail(reviews)
dim(reviews)
nrow(reviews)
ncol(reviews)
str(reviews)
summary(reviews)
names(reviews)
```

## **Data Cleaning(Apps)**

```{r}
colSums(is.na(apps))

apps <- apps %>% filter(Rating <= 5)
apps <- apps %>% drop_na(Rating)

apps$Installs <- gsub("[+,]", "", apps$Installs)
apps$Installs <- as.numeric(apps$Installs)

apps$Price <- gsub("[$]", "", apps$Price)
apps$Price <- as.numeric(apps$Price)

apps <- distinct(apps)
apps <- na.omit(apps)
```

## **Data Cleaning(Reviews)**

```{r}
colSums(is.na(reviews))

reviews <- na.omit(reviews)
reviews <- distinct(reviews)

reviews$Sentiment <- as.factor(reviews$Sentiment)
```

## **Merge Datasets**

```{r}
df <- merge(apps, reviews, by="App")

head(df)
dim(df)
```

## **Visualisation**

```{r}
ggplot(df, aes(x=Category)) + geom_bar(fill="blue")
ggplot(df, aes(x=Rating)) + geom_histogram(fill="green", bins=30)
ggplot(df, aes(x=Sentiment)) + geom_bar(fill="orange")
ggplot(df, aes(x=Sentiment_Polarity)) + geom_histogram(fill="purple")
```

## **Univariative Analysis**

```{r}
table(df$Category)
table(df$Sentiment)
prop.table(table(df$Sentiment))

summary(df$Rating)
summary(df$Installs)

mean(df$Rating)
median(df$Rating)
sd(df$Rating)
```

## **Graphs(Apps)**

```{r}
# Category distribution
ggplot(df, aes(x=Category)) +
  geom_bar(fill="blue") +
  theme(axis.text.x = element_text(angle=90))

# Rating distribution
ggplot(df, aes(x=Rating)) +
  geom_histogram(fill="green", bins=30)
```

## **Graphs(Reviews)**

```{r}
# Sentiment
ggplot(df, aes(x=Sentiment)) +
  geom_bar(fill="orange")

# Polarity
ggplot(df, aes(x=Sentiment_Polarity)) +
  geom_histogram(fill="purple")
```

## **Bivariative Analysis**

```{r}
# Rating vs Category
ggplot(df, aes(x=Category, y=Rating)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle=90))

# Sentiment vs Polarity
ggplot(df, aes(x=Sentiment, y=Sentiment_Polarity)) +
  geom_boxplot(fill="red")
```

## **Corelation**

```{r}
cor(df$Rating, df$Sentiment_Polarity)
cor(df$Sentiment_Polarity, df$Sentiment_Subjectivity)
```

## **Group Analysis**

```{r}
df %>%
  group_by(Category) %>%
  summarise(avg_rating = mean(Rating),
            total_apps = n())

df %>%
  group_by(Sentiment) %>%
  summarise(avg_polarity = mean(Sentiment_Polarity))
```

## **Additional Analysis**

```{r}
summary(df$Price)

table(head(df$Type, 20))

length(unique(df$Category))

max(df$Rating)
min(df$Rating)

df <- df %>% mutate(high_rating = ifelse(Rating > 4.5, "Yes", "No"))
table(df$high_rating)
```

## **Filtering**

```{r}
top_apps <- df %>% arrange(desc(Rating)) %>% head()

cheap_apps <- df %>% filter(Price == 0)

high_polarity <- df %>% filter(Sentiment_Polarity > 0.5)
```

## **Sorting**

```{r}
df %>% arrange(desc(Sentiment_Polarity)) %>% head()
df %>% arrange(Sentiment_Polarity) %>% head()
```

## **Analysis**

```{r}
summary(df$Rating)
summary(df$Installs)

table(df$Category)
table(df$Sentiment)

length(unique(df$App))
```

## **New Column**

```{r}
df <- df %>% mutate(popularity = ifelse(Installs > 1000000, "High", "Low"))
table(df$popularity)
```

## **Statistics**

```{r}
mean(df$Rating)
median(df$Rating)
sd(df$Rating)

range(df$Rating)
quantile(df$Rating)
```

## Insights

-   Most apps belong to categories like GAME and FAMILY\
-   Majority of reviews are positive\
-   Higher rated apps tend to have better sentiment\
-   Free apps dominate the dataset\
-   Sentiment polarity shows user satisfaction trends

## Conclusion

This analysis combines app data and user reviews to understand the relationship between app performance and user sentiment. The results show that higher-rated apps generally receive more positive feedback.
